Repeatability Test

### 2017-09-22 pt_characterization/rep_check/res1.tex
09/22 draft

\paragraph{Fitting the Histograms in Bi-normal Distributions:}
We ran Rob's code to obtain a bi-normal fit for each INC's run. 
Table~\ref{tab:binormal_fit} exhibits the two means (modes), standard deviations, and scales for each of the INC runs.

@@

>>>>

\paragraph{Fitting Histograms in Bi-Normal Distributions:}
We ran Rob's code to obtain a bi-normal fit for each INC's run. 
Table~\ref{tab:binormal_fit} exhibits the two means (modes), standard deviations, and scales for each of the INC runs.

@@

\pagebreak
\clearpage

\begin{figure}[htp!]
	\centering
	\subfigure[Mean]{
		\includegraphics[scale=0.6]{u_s_time/binormal_fit_mean.eps}
		\label{fig:binormal_mean}
	}
	\subfigure[Standard Deviation]{
		\includegraphics[scale=0.6]{u_s_time/binormal_fit_std.eps}
		\label{fig:binormal_std}
	}
	\subfigure[Scale]{
		\includegraphics[scale=0.6]{u_s_time/binormal_fit_scale.eps}
		\label{fig:binormal_scale}
	}
	\caption{Plots of two means, standard deviations, and scales for each INC 
	over increasing task length: based on Table~\ref{tab:binormal_fit}\label{fig:bnormal_Fit}}
\end{figure}
